Explaining the reportedly over-massive black holes in early-type galaxies with intermediate-scale discs

### 2015-11-11 papers/ellicular/MNRAS/ellicular.tex
wed

carter1987,capaccioli1987,capaccioli1988,bender1988,bender1990,
nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
simienmichard1990}. 

@@

@@

whereas other central fast rotators become slow rotating in their outer regions.
A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
is a signature of a large-scale disc, 
while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 

@@

\section{Acknowledgments}
This research was supported by Australian Research Council funding through grant FT110100263. 
GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
We are grateful to our anynimous referee for their very careful review of our paper, 
and for the comments, corrections and suggestions that ensued. 
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA, 
and also on observations made with the NASA/ESA Hubble Space Telescope, 
and obtained from the Hubble Legacy Archive, 
which is a collaboration between the Space Telescope Science Institute (STScI/NASA), 
the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}

>>>>

carter1987,capaccioli1987,capaccioli1988}. 

@@

The same is true when searching for pointy isophotes that are shaped by the combination of the spheroid and a near edge-on disc 
(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,ebneter1987,BenderMoellenhoff1987,bender1988,bijaoui1989}). \\

@@

whereas other central fast rotators become slow rotating in their outer regions\footnote{As pointed out by \cite{cappellari2011}, 
while all of the disky ellipticals from \cite{Bender1994} are fast rotators, 
the complement is not true because weak discs only impact the isophotal shape if the discs have orientations close to edge-on, 
whereas their rotational signature can still be detected when they have a near face-on orientation.  
Of course if a disc is face-on, then the galaxy will not be classified as a fast rotator. }.
%A specific angular momentum profile that is rapidly increasing beyond 1--2 half-light radii 
%is a signature of a large-scale disc, 
%while a specific angular momentum profile that increases up to 1--2 half-light radii and then declines beyond that point 
%indicates the presence of an intermediate-scale disc that no longer dominates at large radii. 

@@

\section{Acknowledgments}
This research was supported by Australian Research Council funding through grant FT110100263. 
GS is grateful to Matteo Fossati, Luca Cortese and Giuseppe Gavazzi for useful comments and discussion. 
The publication of this paper would not have been possible without the invaluable support of 
Chris Blake and Duncan Forbes. 
We warmly thank our anynimous referee for their very careful review of our paper, 
and for the comments, corrections and suggestions that ensued. 
This work is based on observations made with the IRAC instrument \citep{fazio2004IRAC} on-board the Spitzer Space Telescope, 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology under a contract with NASA, 
and also on observations made with the NASA/ESA Hubble Space Telescope, 
and obtained from the Hubble Legacy Archive, 
which is a collaboration between the Space Telescope Science Institute (STScI/NASA), 
the Space Telescope European Coordinating Facility (ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).
This research has made use of the GOLDMine database \citep{goldmine} and the NASA/IPAC Extragalactic Database (NED) 
which is operated by the Jet Propulsion Laboratory, California Institute of Technology, 
under contract with the National Aeronautics and Space Administration.

%\bibliography{/Users/gsavorgnan/galaxy_vivisection/papers/SMBHbibliography}
\bibliography{SMBHbibliography}

### 2015-11-11 papers/ellicular/ellicular.tex
wed

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
%with the latter composed of a spheroidal stellar system encased within a larger, but flatter, stellar disc. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
%intermediate between that of elliptical and lenticular galaxies, which we refer to as \emph{ellicular} galaxies for ease of reference. 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

\citep{liller1966,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
carter1987,capaccioli1987,capaccioli1988,stromstrom1978,bender1988,bender1990,
nieto1988,rixwhite1990,vandenbergh1990,scorzabender1990,scorzabender1995,
simienmichard1990}. 
Not surprisingly, it is well known that 

@@

(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,BenderMoellenhoff1987}). 
Today, most early-type galaxies are classified as ``fast rotators\footnote{The term 
``fast rotator'' is of course not new for describing certain early-type galaxies (e.g.~\citealt{bertinstiavelli1984,lakedressler1986}).}'' 

@@

@@

In general, stellar discs are intrinsically flat and close to circular \citep{Andersen2001,AndersenBershady2002}; 

>>>>

\begin{abstract}
{\bf The classification ``early-type'' galaxy includes both elliptically- and lenticular-shaped galaxies. 
Theoretically, the spheroid-to-disc flux ratio of an early-type galaxy can assume any positive value,  
but in practice studies often consider only spheroid/disc decompositions 
in which the disc neatly dominates over the spheroid at large galaxy radii, 
creating an inner ``bulge'' as observed in most spiral galaxies. 
Here we show that decompositions in which the disc remains embedded within the spheroid, 
labelled by some as ``unphysical'',  
correctly reproduce both the photometric and kinematic properties of early-type galaxies 
with intermediate-scale discs. 
Intermediate-scale discs have often been confused with large-scale discs and incorrectly modelled as such; 
when this happens, the spheroid luminosity is considerably underestimated. 
This has recently led to some surprising conclusions, 
such as the claim that a number of galaxies with intermediate-scale discs (Mrk 1216, NGC 1277, NGC 1271, and NGC 1332) 
host a central black hole whose mass is abnormally large compared to expectations from the (underestimated) spheroid luminosity. 
We show that when these galaxies are correctly modelled, 
they no longer appear as extreme outliers in the (black hole mass)-(spheroid mass) diagram. 
This not only nullifies the need for invoking different evolutionary scenarios for these galaxies 
but it strengthens the significance of the observed (black hole mass)-(spheroid mass) correlation 
and confirms its importance as a fundamental ingredient for theoretical and semi-analytic models 
used to describe the coevolution of spheroids and their central supermassive black holes. }

@@

\citep{liller1966,stromstrom1978,michard1984,djorgovski1985,jedrzejewski1987,BenderMoellenhoff1987,
carter1987,capaccioli1987,capaccioli1988}. 
It is well known that 

@@

(e.g.~\citealt{carter1978,carter1987,jedrzejewski1987,ebneter1987,BenderMoellenhoff1987,bender1988,bijaoui1989}). \\
Today, most early-type galaxies are classified as ``fast rotators'' 

@@

In general, stellar discs are intrinsically flat and close to circular (e.g.~\citealt{Andersen2001,AndersenBershady2002}); 

@@
